---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rMatching

<!-- badges: start -->

<!-- badges: end -->

## Installation

You can install the development version of rMatching from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MatthiasUckert/rMatching")
```

## Build-In Tables

Below The basic steps how to match two data sets

```{r example}
library(rMatching); library(tidyverse)
```

The package contains three build-in datasets:

-   table_source: The source table with company names

-   table_target: The target table with company names

-   table_matches: A table in which source and target table are already matched

```{r}
head(table_source, 3)
```


```{r}
head(table_target, 3)
```


```{r}
head(table_matches, 3)
```

# Matching Pipeline

## Step 1: Prepare Tables

Tables have to b prepared with the function: prep_tables()

Important: Specify the columns you want to match in the argument **.col**. This must be a named vector (**e** for **exact matching** and **f** for f**uzzy matching**)

```{r}
prep_tables(
  .source = table_source,
  .target = table_target,
  .cols = c(f = "name", e = "iso3", f = "city", f = "address"),
  .fstd = standardize_str,
  .dir = "_debug_data1",
  .range = 10
)
```

The relevant tables are stored in the directory (.dir)

```{r}
tibble(file = list.files("_debug_data1/tables/")) %>%
  mutate(type = case_when(
    startsWith(file, "s") ~ "Source Table",
    startsWith(file, "s") ~ "Target Table",
    TRUE ~ "Groups"
  )) %>% select(type, file)

```

## Step 2: Match Data
For match_data() you have to reference the directory and the method used for matching
```{r}
match_data(
  .dir = "_debug_data1",
  .max_match = 20,
  .method = "osa",
  .workers = 4,
  .verbose = TRUE
)
```

Here we match over all methods
```{r}
purrr::walk(get_method_names(), ~ match_data("_debug_data1", 20, .x, 4, TRUE))
```

## Step 3: Score Data
For score_data() you have to give the fuzzy matching columns some weights
```{r}
w <- c(name = .8, city = .1, address = .1)
score_data(
  .dir = "_debug_data1",
  .weights = w ,
  .max_match = 20,
  .method = "osa"
)
```

Here we score over all methods
```{r}
purrr::walk(get_method_names(), ~ score_data("_debug_data1", w, 20, .x))
```

## Step 4: Score Data
select_data() is the only functions that returns a dataframe directly.
You can choose up to which rank you retrueve the data.
We directly match over all methods.
```{r}
tab_match <- purrr::map_dfr(
  .x = get_method_names(),
  .f = ~ select_data(
    .dir = "_debug_data1",
    .rank = 1,
    .method = .x
  ), .id = "method"
)
```

# Matching Comparison
```{r}
.matches <- select(mutate(table_matches, match = 1), id_s, id_t, match)
tab_comparison <- left_join(tab_match, .matches, by = c("id_s", "id_t")) %>%
  replace_na(list(match = 0)) %>%
  group_by(method) %>%
  summarise(p = sum(match) / n())
```

```{r}
tab_comparison %>%
  mutate(label = scales::percent(p, .1)) %>%
  ggplot(aes(method, p)) + 
  geom_col(fill = "blue", color = "black") + 
  ggthemes::geom_rangeframe() + 
  ggthemes::theme_tufte() +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = label), vjust = 1.5, colour = "white", size = 3.5)
```

# Legal Form Adjustment
We can also adjust the lagel form upfront, and will do so for the bedt method "jw"

```{r}
tab_source_lf <- extract_legal_form(
  .tab = table_source,
  .col = "name",
  .workers = 4
)

tab_target_lf <- extract_legal_form(
  .tab = table_source,
  .col = "name",
  .workers = 4
)
```

```{r}
head(tab_source_lf, 3)
```


```{r}
head(tab_target_lf, 3)
```

Now we use the name_adj column for the matching which is the company name without its legal form.
Additionally, we also fuzzy match on the legal form (we have to fuzzy match, because requiring exactly the same legal form is to strict)
```{r}
prep_tables(
  .source = tab_source_lf,
  .target = tab_target_lf,
  .cols = c(f = "name_adj", e = "iso3", f = "city", f = "address", f = "lfs"),
  .fstd = standardize_str,
  .dir = "_debug_data2",
  .range = 10
)
```

```{r}
match_data(
  .dir = "_debug_data2",
  .max_match = 20,
  .method = "jw",
  .workers = 4,
  .verbose = TRUE
)
```

```{r}
w <- c(name_adj = .8, city = .1, address = .05, lfs = .05)
score_data(
  .dir = "_debug_data2",
  .weights = w ,
  .max_match = 20,
  .method = "jw"
)
```


```{r}
tab_match_lf <- select_data(
  .dir = "_debug_data1",
  .rank = 1,
  .method = "jw"
) %>%
  mutate(method = "jw-lf") %>%
  bind_rows(tab_match)
```

# Matching Comparison
```{r}
.matches <- select(mutate(table_matches, match = 1), id_s, id_t, match)
tab_comparison <- left_join(tab_match_lf, .matches, by = c("id_s", "id_t")) %>%
  replace_na(list(match = 0)) %>%
  group_by(method) %>%
  summarise(p = sum(match) / n())
```

```{r}
tab_comparison %>%
  mutate(label = scales::percent(p, .1)) %>%
  mutate(fill = if_else(method == "jw-lf", "red", "blue")) %>%
  ggplot(aes(method, p, fill = fill)) + 
  geom_col(color = "black") + 
  scale_fill_manual(name = "method", values=c("blue","darkred")) +
  ggthemes::geom_rangeframe() + 
  ggthemes::theme_tufte() +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = label), vjust = 1.5, colour = "white", size = 3.5) + 
  theme(legend.position = "none")
```
